Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-07 02_Paper/paper.tex
Predictive analytics in production

According to Delen and Damirkan, predictive analytics (PA) unravel the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
PA offers a wide range of applications, and it can be implemented as long as the provided data are sufficiently available. By considering the industrial and production environment, PA would be a great asset due to the high flexibility and high amount of data available coming from processes, single machines or cells, products, and others. Some common industrial applications of PA in the industry are focused products (design and optimization), machines (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.

Applications that combine PA with QC might improve the current QC processes. By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process.

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications in this area. Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}, and Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.

>>>>

According to Delen and Damirkan, predictive analytics (PA) consists of unraveling the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
PA offers a wide range of applications, and it can be implemented, as long as the provided data are sufficiently available \cite{bishop2006pattern}.
According to Krauß, there is a wide range of applications for PA in the industrial and production environment. Some common industrial applications of PA in the industry are focused products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control)\cite{krauss2019machine}

Applications that combine PA with QC might improve the current QC processes. By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications in this area. Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
